--- 
title: "Econometrics visualization"
author: "Lucas Chaveneau, Thibault Fuchez, Allan Guichard"
date: "`r Sys.Date()`"
documentclass: report
bibliography: references.bib
biblio-style: apalike
link-citations: yes
description: First try of bookdown
site: bookdown::bookdown_site
---

# Introduction

```{r eval=FALSE, include=FALSE}
bookdown::serve_book()
```


```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
## What is Econometrics?

<<<<<<< HEAD
Econometrics is a branch of economics that aims to estimate and test economic models (simplified representation of reality). Thus, the econometer tries to identify the parameters of a model by means of statistical estimation, and thus tries to induce the characteristics of a general group (the population) from those of a particular group (the sample).
=======
BLABLABLA

Econometrics is a branch of economics that aims to estimate and test economic models (simplified representation of reality). Thus, the econometrician tries to identify the parameters of a model by means of statistical estimation, and thus tries to induce the characteristics of a general group (the population) from those of a particular group (the sample).
>>>>>>> deedb0dc1cd0094bc1d3cb0eaf99e5e078b9f27a

Three essential words in the language of the econometer are: correlation, regression, and causality.

To better understand the relationships between different variables, visualization is a key tool to help interpret mathematical and statistical results.

## What about econometric visualization?

We can start by saying what it is not: it is not strictly speaking data visualization.
Data visualization "the graphical display of data" is often seen as something trivial, to be quickly scrolled through to show stakeholders simple but salient facts of a possibly very complex problem...

The analyst consciously chooses what to include in a visualization in order to identify intuitively relevant patterns and trends in the data in the most efficient way. The analyst then makes choices in this representation. Modern data sets tend to be very large (in terms of number of observations) and broad (in terms of number of variables). Therefore, it is hard to simply represent all the data. The difficulty is that everything must be made as simple as possible - but not simpler.

Visualization is used to explain, notably to teach, econometrics in order to facilitate the understanding of the fundamental concepts without necessarily using a mathematically complex corpus.
Diagrammatic representations of models, methods and diagrams can facilitate the understanding and reading of results.

## State of the art

Data visualization is an important part of any statistical analysis. Any good statistician will tell you that it is dangerous to undertake an econometric analysis without first examining the data. 
Scatterplots are used as a tool to diagnose the overall trend, the relationship between variables, the variation around the perceived trend, the exceptions whether they are outliers or distinct groups of observations, the discontinuities. The analysis of residuals largely uses the same tools.

A bibliographic search on the theme of visualization in econometrics does not yield much. Nevertheless, we will mention in this document some articles that deal with the subject in a direct or indirect way, and that have been an anchor point in our reflections.

Moreover, some packages related to econometric visualization have already been developed in R (or other languages). At the end of this document, we will briefly describe the state of the art of these packages.


## Our project, an R package

Our project stands to propose a library developed under R which proposes different ways to visualize the essential elements of the econometer. 

Our package will therefore focus on the representation of correlations. We will try to put forward a clear and synthetic representation of the covariance, a representation of the elements that allow to visualize the quality of a regression, as well as the part of each variable in the explanation of the variable to predict.

This document is intended to be a guide for the package. It proposes a definition of the econometric tools usefull to understand the package. It also proposes an overview of the different visualization methods that already exist. 








